Building a continuous benchmarking ecosystem in bioinformatics

### 2025-02-07 review_cycle_1/highlighted_manifesto_main.tex
add placeholders

Benchmarks can also be of high value to \emph{scientific journals} and \emph{funding agencies}. Well-executed benchmark studies can be highly utilized and influential, and may point to gaps in the current body of methods, guiding future methodological developments; at the same time, in fast-moving fields like bioinformatics, benchmarks have the tendency to rapidly become stale. Journals and funding bodies also have a vested interest in ensuring that published or funded method developments are performed to a high standard, that unnecessary redundancy is reduced, and that results are FAIR (findable, accessible, interoperable and reusable) for maximal benefit to the community \cite{Wilkinson2016-bh}. Thus, quality assurance, neutrality and transparency of benchmarking systems become highly relevant.

@@

Benchmarking as a process deals with tasks other than workflow definition and execution, including: collecting and keeping track of contributions from users; provisioning appropriate hardware; handling a reproducible and efficient software stack; managing storage and access-control lists; rendering results dashboards and summarizing results; versioning code, workflow runs, and files; and providing extensive documentation from defining scope or contribution guidelines, to transparent logging and crediting contributions and disseminating results.

@@

>>>>

Benchmarks can also be of high value to \emph{scientific journals} and \emph{funding agencies}. Well-executed benchmark studies can be highly utilized and influential, and may point to gaps in the current body of methods, guiding future methodological developments; at the same time, in fast-moving fields like bioinformatics, benchmarks have the tendency to rapidly become stale. Journals and funding bodies also have a vested interest in ensuring that published or funded method developments are performed to a high standard, that unnecessary redundancy is reduced, and that results are FAIR (findable, accessible, interoperable and reusable) for maximal benefit to the community \cite{Wilkinson2016-bh}. {\color{red} Recently published benchmarks and challenges have been conceived as or ported to benchmarking systems to ensure these properties.} Thus, quality assurance, neutrality and transparency of benchmarking systems become highly relevant.

{\color{red} Discuss DREAM, CASP etc and scientific communities here (reviewer 1 and 2).}

@@

Benchmarking as a process deals with tasks other than workflow definition and execution, including: collecting and keeping track of contributions from users; provisioning appropriate hardware; handling a reproducible and efficient software stack; managing storage and access-control lists; rendering results dashboards and summarizing results; versioning code, workflow runs, and files; and providing extensive documentation from defining scope or contribution guidelines, to transparent logging and crediting contributions and disseminating results {\color{red}(Figure~\ref{fig:definitions})}.

@@

{\color{red} Here all content on whether software is part of the backend or not, conda, pixi, web assembly etc - reviewer 3}
